\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\newcommand{\Header}{
  \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{http://\PersonalWebsite}{\Huge{\Name}}} & \textbf{\LARGE Contact}\\
  Learn more at: \href{http://\PersonalWebsite}{\PersonalWebsite} & Write me at: \href{mailto:\PersonalEmail}{\PersonalEmail}\\
  Connect with me at: \href{https://\LinkedIn}{\LinkedIn} & Talk to me at: \PhoneNumber \\
  See what I'm working on at: \href{https://\Github}{\Github} & Find me at: \Location
  \end{tabular*}\vspace{-5pt}
}

%-------------------------------------------  
%------ RESUME STARTS HERE, Enter your information here!!  
%-------------------------------------------
%------------- Setting User Data
\newcommand{\Name}{Eduardo Escoto}
\newcommand{\PersonalWebsite}{eduardoescot.io}
\newcommand{\LinkedIn}{linkedin.com/in/e-esc}
\newcommand{\Github}{github.com/eduardoescoto}
\newcommand{\PersonalEmail}{e.esc@eduardoescot.io}
\newcommand{\PhoneNumber}{+1 (858) 357-1868}
\newcommand{\Location}{Isla Vista, CA}


\begin{document}
%----------HEADING-----------------
\Header

%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {\large University of California, Santa Barbara}{Santa Barbara, CA}
      {Bachelor of Science in Mathematical Science and Statistical Science}{September 2017 -- June 2020}
      \resumeItemListStart
        \resumeItem{Concentration}
        {Probability and Statistics}
        \resumeItem{Organizations}
          {Data Science club, Association for Women in Mathematics}
          \resumeItem{Relevant Coursework}
          {Data Science, Regression Analysis, Stochastic Systems, Real Analysis, Linear Algebra}
      \resumeItemListEnd
    \resumeSubheading
      {\large San Diego Miramar College}{San Diego, CA}
      {Associate of Science in Mathematics and Computer Science}{September 2014 -- June 2017}
      \resumeItemListStart
        \resumeItem{Organizations}
        {Phi Theta Kappa Honors Society}
        \resumeItem{Relevant Coursework}
          {Data Structures, C++, Java, Visual Basic}
        \resumeItem{Accomplishments}
          {Honors Student, Deans List Scholar, Annual Research Symposium Presenter}
      \resumeItemListEnd
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Starbucks Coffee}{San Diego, CA}
      {Shift Supervisor and Barista}{June 2013 -- Present}
      \resumeItemListStart
        \resumeItem{Certified Coffee and Food Master}
          {Succeeded in Coffee and Food master certifications and continued on to win the district Barista Championship in 2016. First Partner of the Quarter at store.}
        \resumeItem{Maintains and Enforces Cleanliness Standards}
          {Monitors store cleanliness in order to upkeep a standard of excellence. Quality and Safety Assessment score raised from a 93\% to a 99\%.}
        \resumeItem{Upholds Drink and Food Standards}
          {Bolstered store's food sales, and led store to win district food sales competition, and a sepatate whole bean coffee sales contest. }
        \resumeItem{Manages Cash, Safe, and Inventory}
          {Counts money for the day and ensures cash is not lost and profits are accounted for. Orders inventory and works towards optimizing storage and minimizing waste.}
          \resumeItem{Prioritizes Stellar Customer Satisfaction}
            {Leads a team of world-class baristas to create a positive, inclusive, and motivating work environment that customers consistently enjoy visiting.}
      \resumeItemListEnd
      \resumeSubheading
        {Biosero Inc.}{San Diego, CA}
        {Software Engineering Intern}{September 2016 -- September 2017}
        \resumeItemListStart
        \resumeItem{Driver Development}
          {Developed drivers for a myriad of Bio-tech instruments for use in automization. These included, Robotic Arms Sealers/Desealers, Acoustic Dispensing Systems, Microplate Readers, and many more.}
        \resumeItem{Product Design and Development}
          {Created Bluetooth Barcode Scanner prototype that would allow for easier, and more flexible microplate tracking. Involved
          modeling the design in Solidworks, developing a custom PCB with Eagle, working closely with a scanner manufacturer to secure bulk sale,
          programming a driver for the scanner, and troubleshooting and testing the product. This project involved the entire product development cycle.}
        \resumeItem{Database and UI/UX Engeering}
          {Engineered and optimized microplate tracking database.
          Developed and tested UI elements and collaborated with designers to clarify, and generate automatic product documentation.}
        \resumeItem{MagneMotion Track Integration}
        {Implemented magnetic track system for use in large scale and connected integrations. Utilized graph theory and queueing theory to streamline track movement algorithm. }
        \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------PROJECTS-----------------
\section{Projects}
  \resumeSubHeadingListStart
    \resumeSubItem{PrettyPastelBot}
      {Twitter bot built in Node that generates a random pastel color and tweets it with its color info.}
    \resumeSubItem{Law of Large Numbers Simulator}
      {Simulator of the Strong Law of Large numbers crafted with React + Redux. Simulates infinite trials of identically distibuted random events to illustrate the effect of the Law of Large Numbers.}
    \resumeSubItem{LOL Esports Data Scraper}
      {Data mining project that scrapes data from Riot’s hidden LOL-Esports-Api, and aggregates the most important player data available into neat json files. Used for Sabermetrics Analysis on players.}
    \resumeSubItem{Superconductor Analysis}
      {Analysis of data gathered from more than 20,000 Superconductors to investigate the efficacy of a regression model in predicting Superconductor Critical Temperatures from elemental composition.}
  \resumeSubHeadingListEnd


% --------PROGRAMMING SKILLS------------
\section{Programming Skills}
 \resumeSubHeadingListStart
   \resumeSubItem{Languages}
    {Python, Javascript, C++, C\#, Java, R, Visual Basic, Shell Scripting, SQL, XAML, HTML, CSS.}
  \resumeSubItem{Technologies and Tools}
    {React, Redux, Apollo, Express, D3, Node, PyTorch, Scikit-learn, NumPy, Pandas, Rmarkdown, Shiny, Tidyverse, Firebase, Heroku, Git and Source Control, CLI tools.}
 \resumeSubHeadingListEnd

%-------------------------------------------
\end{document}
