
\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{http://eduardoescot.io/}{\LARGE Eduardo Escoto}} & \textbf{\LARGE Contact}\\
  Learn more at: \href{http://eduardoescot.io/}{eduardoescot.io} & Write me at: \href{mailto:e.esc@eduardoescot.io}{e.esc@eduardoescot.io}\\
  Connect with me at: \href{https://linkedin.com/in/e-esc/}{linkedin.com/in/e-esc} & Talk to me at: +1 (858) 357-1868 \\
  See what I'm working on at: \href{https://github.com/eduardoescoto}{github.com/eduardoescoto} & Find me at: Isla Vista, CA \\
\end{tabular*}


%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {\large University of California, Santa Barbara}{Santa Barbara, CA}
      {Bachelor of Science in Mathematical Science and Statistical Science}{September 2017 -- June 2020}
      \resumeItemListStart
        \resumeItem{Concentration}
        {Probability and Statistics}
        \resumeItem{Organizations}
          {Data Science club, Association for Women in Mathematics}
          \resumeItem{Relevant Coursework}
          {Data Science, Regression Analysis, Stochastic Systems, Real Analysis, Linear Algebra}
      \resumeItemListEnd
    \resumeSubheading
      {\large San Diego Miramar College}{San Diego, CA}
      {Associate of Science in Mathematics and Computer Science}{September 2014 -- June 2017}
      \resumeItemListStart
        \resumeItem{Organizations}
        {Phi Theta Kappa Honors Society}
        \resumeItem{Relevant Coursework}
          {Data Structures, C++, Java, Visual Basic}
        \resumeItem{Accomplishments}
          {Honors Student, Deans List Scholar, Annual Research Symposium Presenter}
      \resumeItemListEnd
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Starbucks Coffee}{San Diego, CA}
      {Shift Supervisor and Barista}{June 2013 -- Present}
      \resumeItemListStart
        \resumeItem{Maintains and Enforces Cleanliness Standards}
          {I lead the way in store cleanliness in order to maintain a standard of excellence, where my efforts boosted our Q.A.S.A score from a 93\% to a 99\%}
        \resumeItem{Upholds Drink and Food Standards}
          {As a certified Coffee and Food Master I bolstered my store's food sales, and led us to win the district food sales competition.}
        \resumeItem{Coffee and Food Master}
          {Succeeded in the Coffee and Food master certifications and went on to win my district's Barista Championship in 2016, additionally I was the first partner of the quarter at my store.}
        \resumeItem{Maintains Stellar Customer Satisfaction}
          {I lead a team of world-class baristas to deliver a customer experience like no other. I aim to create a positive, inclusive, and motivating work environment that customers enjoy visiting.}
        \resumeItem{Cash, Safe, and Inventory Management}
          {I count the money for the day and ensure cash is not lost and profits are accounting for. I also order inventory and am working towards minimizing waste.}
      \resumeItemListEnd
      \resumeSubheading
        {Biosero Inc.}{San Diego, CA}
        {Software Engineering Intern}{September 2016 -- September 2017}
        \resumeItemListStart
        \resumeItem{Driver Development}
          {Developed drivers for a myriad of Bio-tech instruments for use automization. These included, Robotic Arms Sealers/Desealers, Acoustic Dispensing Systems, Microplate Readers, and many more.}
        \resumeItem{Product Development}
          {Created idea for a Bluetooth Barcode Scanner that would allow for easier, and more flexible microplate tracking. This involved
          modeling the design in Solidworks, developing a custom pcb with Eagle, working closely with a scanner manufacturer to secure bulk sale,
          programming a driver for the scanner, and troubleshooting and testing it. This project took me through the entire product development cycle.}
        \resumeItem{Database and UI Design}
          {Worked on microplate tracking database and optimized database structure.
          Also developed and tested UI elements and collaborated with our designer to write documentation on how to use the UI.}
        \resumeItem{MagneMotion Track Development}
        {Worked to implement a magnetic track system for use in large scale and connected integrations. Used graph theory and queueing theory to optimize track movement algorithm. }
        \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------PROJECTS-----------------
\section{Projects}
  \resumeSubHeadingListStart
    \resumeSubItem{PrettyPastelBot}
      {Twitter bot written in node that generates a random pastel color and tweets it with its color info.}
    \resumeSubItem{Law of Large Numbers Simulator}
      {A simulator of the Strong Law of Large numbers made with React + Redux. Simulates infinite random trials of random events to illustrate the effect of the LOLNS.}
    \resumeSubItem{LOL Esports Data Scraper}
      {A data mining project that scrapes data from Riot’s hidden LOL-Esports-Api, and aggregates the most important player data available into neat json files.}
    \resumeSubItem{Superconductor Analysis}
      {In this project I analyzed data gathered from more than 20,000 superconductors to see if we can predict a superconductor’s critical temperature using regression.}
  \resumeSubHeadingListEnd


% --------PROGRAMMING SKILLS------------
\section{Programming Skills}
 \resumeSubHeadingListStart
   \resumeSubItem{Languages}
    {Python, Javascript, C++, C\#, Java, R, SQL, HTML, CSS, Shell Scripting.}
  \resumeSubItem{Technologies}
    {React, Redux, Express, D3, Node, Git, PyTorch, XAML, Rmarkdown, Tidyverse, Shiny, CLI tools.}
 \resumeSubHeadingListEnd


%-------------------------------------------
\end{document}
